%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Reference:
% Debarghya Das (http://debarghyadas.com)

\documentclass[]{hieudo-build}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Carlos Flores}
{\urlstyle{same}    
 \href{mailto:carlos42044@gmail.com}{ carlos42044@gmail.com}\hspace*{-10cm}\\
\hspace*{.11cm}{908-499-8332}\\
\href{https://github.com/carlos42044}{ github.com/carlos42044}\\
\href{https://www.linkedin.com/in/carlosfloresjr}{ in/carlosfloresjr}
}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN ONE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.34\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection{Kean University}
\descript{Union, NJ}
B.S. Computer Science, May 2018 \\
GPA 3.9/4.0  \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
% \subsection{Programming}
\location{Programming Languages:}
Most Experience: Java\\
Some Experience: Groovy, Go, Python, Bash\\
\iffalse
\location{Frameworks:}
AngularJS, jQuery, Ionic, 
NodeJS, Karma/Jasmine/Protractor \\
\fi
\location{Technologies:}
Git, Spring framework\\

\location{Languages:}
Fluent Spanish \\
 

% \sectionsep
% \subsection{Languages}
% \location{Native fluency:} English, \\
\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     HACKATHONS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Hackathons}
% HackMIT \textbullet{} hackNY \\
% WearHacks NY  \\
% \sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ADDITIONAL INFORMATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Leadership}
- President of Kean University's ACM Student Chapter (2017-2018)\\
- Co-Director of HackKean 2018\\
- Computer Science Tutor - Kean University (2016 - 2018)\\
\sectionsep

\section{Awards}
- NSF CS S-STEM Scholarship \\
\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Competitive academic merit scholarship from NSF
\end{tightemize}
- Dean's List 5/5 Semesters \\
- Tapia 2017 Conference scholarship recipient 
\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     AWARDS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% Dean's List\\

% \sectionsep

\sectionsep
\iffalse
\DTMsetdatestyle{mylastupdate}
\DTMdisplaydate{\the\year}{\the\month}{\the\day}{-1}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN TWO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.65\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\workplace{Bank of New York Mellon}{June 2018 – Present}\\
\position{Technology Leadership Program, Software Engineer}{Jersey City, NJ}
\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Integrated a CLI served over web browser written in Go (open source project) with the firm's large internal PAAS system. 
\item Added functionality to several business critical microservices used in a large internal PAAS serving hundreds of internal applications.  
\item Assisted teaching in several PAAS/Docker workshops to internal developers on how to deploy apps using our PAAS and how to build more resilient applications.
\item Developed a microservice using groovy and Spring to operate on and transform files stored in Amazon S3.
\item Worked with Open Policy Agent to write several policies used to build a service allowing internal app teams to easily perform centralized role management and entitlements checks in their applications. 
\item Administered several technical interviews to prospective summer interns for BNY's Summer Analyst Program.
\end{tightemize}
\sectionsep

\workplace{Compuflex Corporation}{June 2017 – August 2017}\\
\position{Student Intern}{Springfield, NJ}
\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed 2 Point of sales systems (POS) that were used as a testing tool to develop a large screen management system.
\item The 2 applications were developed for Windows OS. (WinForms GUI and WPF GUI).  
\item Wrote detailed documentation of the POS systems for future reference. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects/Hackathons}
\runsubsection{mARked}
\descript{iOS Application}
Built the back end for an augmented reality social media app on top of Amazon Web Services. Utilized Amazon Cognito, AWS Lambda, Amazon API Gateway, 
Amazon Relational Database Service (MySQL), and AWS Mobile Hub services.

\sectionsep 

\runsubsection{Loan It}
\descript{}
An android app that displays loan amortization schedule. Aims to promote education and financial awareness of loan lending. Developed using Android Studio.
\sectionsep 

% \runsubsection{DecideForMe}
% \descript{(Hack Cooper NYC, 2016)}
% iOS app that shows relevant places to sightsee/eat based on an user's tweet activity. Team project built with the Ionic framework and Twitter/Yelp/Google Maps API. I developed the front end using HTML/CSS.
% \sectionsep 

\end{minipage} 

\end{document}  
